Interested in joining the team

### 2025-01-20 index.qmd
open application period

<font color="#d08770">[October 21 2024].</font> **New milestone**. Congratulations to Nour Al Afif on successfully defending her MSc work. We are excited that Nour is staying in the lab for her doctoral studies.

<font color="#d08770">[September 18 2024].</font> **Paper accepted**. Roth, A.M., Buggeln, J.H., Hoh, J., Woods, J.M., Sullivan, S.R., Ngo, T., Calalo, J.A., Lokesh, R., Morton, S.M., Grill, S., Jeka, J.J., Carter, M.J., & Cashaback, J.G.A. Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson's disease. *PLoS Computational Biology*.

<font color="#d08770">[September 05 2024].</font> **New milestone**. Congratulations to Mikayla Lalli on successfully defending her MSc work. We are excited that Mikayla is staying in the lab for her doctoral studies.

<font color="#d08770">[September 03 2024].</font> **Paper accepted**. St. Germain, L., McKay, B., Barbera, L., Tandon, C., Seedu, J., Carrillo, C., Brown, B.M.Y., & Carter, M.J. Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *Psychological Research*.

>>>>

<font color="#d08770">[January 20 2025].</font> **Announcement**. The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year. Please see [https://cartermaclab.org/join](https://cartermaclab.org/join) for details.

### 2025-01-20 join.qmd
open application period

If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to cartem11@mcmaster.ca.

**The application period for practicum, project, and thesis courses for the 2024-25 academic year is now closed.**

Please be aware that volunteer research assistant positions are filled on a rolling basis and as needed.

@@

If you are interested in completing your M.Sc or Ph.D in the lab, please email Dr. Carter (cartem11@mcmaster.ca) an up-to-date curriculum vitae, unofficial academic transcripts, and a 1-page statement of research interests.

>>>>

If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab [at] mcmaster [dot] ca.

<font color="#d08770">**The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year.**</font>

- Applications will be received until Friday, February 28, 2025
- Applicants selected for an interview will be notified by Friday, March 7, 2025
- Interviews will take place in mid-to-late March
- Offers for a practicum, project, or thesis position in the lab will be sent to selected students by Monday, March 31, 2025

Please be aware that volunteer research assistant positions are also filled on a rolling basis and as needed.

@@

If you are interested in completing your M.Sc or Ph.D in the lab, please email Dr. Carter (cartem11 [at] mcmaster [dot] ) an up-to-date curriculum vitae, unofficial academic transcripts, and a 1-page statement of research interests.
